 
 In this section, we show that the explicit Linear Steklov method 
 \eqref{m1}-\eqref{eqn:SolutionFunctions} converges  with a standard order of one-half. For that,
 we use an analogous procedure as in \cite{Higham2002b}.
 
\begin{lem}
	Under \Cref{PolynomialGrowth,ass:MomentBounds} and sufficiently small $h$, there exist
	constants $D'\in \R$ and $q'\in \Z$ such that for all $u,v\in \R^d$
	\begin{align}
		|
			\varphi_{f_h}(u)
			-\varphi_{f_h}(v)
		|^2 
		&\leq
			D'
			\left(
				1 +|u|^{q'} +|v|^{q'}
			\right)
			|u-v|^2, \\
		%
		|
			 f(u) -\varphi_{f_h}(u)
		|^2 
		&\leq
			D'
			\left(
				1 +|u|^{q'} 
				\right)
			h^2, \\
		%
		|
			g(u) -g_h(u)
		|^2 				 
		&\leq
			D'
			\left(
				1 +|u|^{q'} 
			\right)
			h^2 . \label{eqn:ghPolyGrowth}
	\end{align}
\end{lem}

\begin{pf}
	From relationship \eqref{fo} and inequality \eqref{eqn:PhifhFbound}, we have
	\begin{equation*}
		|\varphi_{f_h}(u) - \varphi_{f_h}(v)|^2
		\leq
			(2 + L_{\Phi}) |f(u) - f(v)|^2 
			\leq
				(2 + L_{\Phi}) D (1 + |u|^q +|v|^q). 
	\end{equation*}
	Moreover, if $u \in E_j$ then $\varphi_{f_h}(u) = f^{(j)}(u)$. On the other hand,  if $u\in E_j^c$ then
	$$
		|f(u) - \varphi_{f_h}(u)|^2
		=
		\sum_{j=1}^d
			|1-\Phi_j(u)|^2 |f^{(j)}(u)|^2,	
	$$
	 By the L'H\^{o}pital 
	theorem, we get
	\begin{align*}
		\lim_{h \to 0} |1-\Phi_j(u)| 
			&= \left|
				1-\lim_{h\to 0} \frac{e^{h a_j(u)}-1}{h a_j(u)}
			\right|			
			\leq 
				\left|
					1-\lim_{h\to 0} e^{h L_a}
				\right|=0.			
	\end{align*}
	Thus there is a sufficiently small $h>0$  such that
	$|1-\Phi_j(u)|<C h$ for all $u\in E_j^c$ and
	$$
		|f(u) - \varphi_{f_h}(u)|^2
		\leq
		Ch^2 |f(u)|^2
		\leq D'(1+|u|^q)h^2,	
	$$
	as we require. Meanwhile, given that $g_h(u)=g(F_h(u))$ from \Cref{lem:PhiFhProp} it is followed
	\begin{equation*}
		|g(u) - g_h(u)|^2 
		\leq
			L_g |u - u +h \varphi{f_h}(u)|^2 
		\leq 
			2(1+L_{\Phi})h^2 |f(u)|^2
		\leq
			2(1+L_{\Phi}) D(1+|u|^q) h^2. 
	\end{equation*}
	\qed
\end{pf}
%
\begin{lem}\label{lem:yhyOh}
	Assume \Cref{PolynomialGrowth,ass:MomentBounds} hold then the solution $y_h(t)$ of 
	the modified SDE \eqref{eqn:PerturbedHighamSDE}
	satisfies
	\begin{equation}
		\EX{
			\sup_{0\leq t \leq T}
			|y_h(t) - y(y)|^2	
		} = \mathcal{O}(h^2).
	\end{equation}	
\end{lem}
\begin{pf}
	We define $e(t):= y(t)-y_h(t)$ where
	\begin{eqnarray*}
		y(t) &=& y_0 + \int_{0}^t f(y(s))ds + \int_{0}^t g(y(s))dW(s),  \nonumber\\
		y_h(t) &=& y_0 + \int_{0}^t \varphi_{f_h}(y_h(s))ds + \int_{0}^t 
		g_h(y_h(s))dW(s).\nonumber
	\end{eqnarray*}
	Using It\^{o}'s formula over the function $V(t,x,y) = |x-y|^2$ for all  $x,y\in \R^d$, we obtain 
$$
		d e(t) = 
		\left(
			f(y(t)) - \varphi_{f_h}(y(t)) dt
		\right)
		+
		\left(
			g(y(t)) - g_h(y_h(t))
		\right) dW(t),
	$$
	Thus
	\begin{align} \label{eqn:IntErrToBound}
		|e(t)|^2 
		&=
			2 \underbrace{\int_{0}^t
				\innerprod{e(s)}{f(y(s))-\varphi_{f_h}(y_h(s))} ds }_{:=I_1}
			+
			\underbrace{\int_{0}^t
				|g(y(s)) - g_h(y_h(s))|^2 ds }_{:=I_2}\notag\\
		&+
			2 \underbrace{\int_{0}^t
				\innerprod{e(s)}{\left[ g(y(s))-g_h(y_h(s)) \right] dW(s)}}_{:=I_3}.	\end{align}
	Now we proceed to bound each integral of inequality \eqref{eqn:IntErrToBound}. 
	By \Cref{PolynomialGrowth}, the Young and  standard 
	inequalities, we get
	\begin{align*}
		I_1(t) 
		&\leq
			2\int_0^t
				\innerprod{y(s) - y_h(s)}{f(y(s))-f(y_h(s))} ds
			+
			 \int_0^t
				 \innerprod{y(s) - y_h(s)}{f(y_h(s))-\varphi_{f}(y_h(s))} ds \notag\\
%	
		&\leq
			3\int_0^t
				|y(s) - y_h(s)|^2ds
			+ D' h^2 
			\int_0^t
				1 + |y_h(s)|^{q'} ds.
	\end{align*}
	Since $y_h(t)$  the has bonded moments, there exists a universal constant $L$ which does not depends on $h$ 
	such that
	\begin{equation}\label{eqn:I1Bound} 
		 \EX{
			 I_1(s)	
		 }
		 \leq
			 L\int_{0}^t
				\m{|e(s)|^2} ds
		+ L h^2.
	 \end{equation}
	Meanwhile, using  \Cref{ass:OSLC,PolynomialGrowth} it is followed
	\begin{align*}
		I_2(t) 
		&\leq
			2 L_g 
			\int_{0}^t
				|y(s) - y_h(s)|^2 ds
			+
			2D'h^2
			\int_0^t
				1 + |y_h(s)|^q ds. 	 
	\end{align*}
	and thus
	\begin{equation} \label{t5}
		\EX{
			I_2(s)	
		}
		\leq
		L\int_{0}^t
		\m{|e(s)|^2} ds
		+ L h^2.
	\end{equation}
	Note that $\EX{ I_3(t)} \leq \EX{ 
				\sup_{0\leq s \leq t}
				|I_3(s)|
			}$.
	From the Burkholder-Davis-Gaundy inequality, \Cref{ass:OSLC,PolynomialGrowth} and 
	as $y_h(t)$ has bounded moments, we see that
	\begin{align}
		\EX{ 
			\sup_{0\leq s \leq t}
			|I_3(s)|
		}
		%
		&\leq
		2^4 
		\EX{
			\sup_{0 \leq s \leq t}
			|e(s)|^2
			\int_{0}^t
				|g(y(s))-g_h(y(s))|^2 ds
		}^{1/2} \notag \\
		&\leq
		2^4 
		\EX{
			\frac{1}{2 \cdot 2^9}
			\left(
				\sup_{0\leq s \leq t}
				|e(s)|^2
			\right)			
			+
			\frac{2^9}{2}
			\left(
				\int_{0}^t
					|g(y(s)) - g_h(y_h(s))|^2 ds
			\right)^2
		}
		\notag \\
		%
		&\leq
			\frac{1}{2}
			\EX{
				\sup_{0 \leq s \leq t}
				|e(s)|^2
			}
		+2^8
		\EX{
			\int_{0}^t
				|g(y(s)) - g_h(y_h(s))|^2	
			ds
		}\notag\\
		%
		&\leq
			2 L_g
			\EX{
				\int_{0}^t
					|y(s) - y_h(s)|^2 ds		
				} 
			+D'Th^2 
			+
			D'Th^2
			\int_{0}^t
				\m{|y_h(s)|^{q'}} ds 	
		\notag \\
		&\leq
			L
			\int_{0}^t
				\m |e(s)|^2 ds
			+L h^2. \label{eqn:I3Bound}
	\end{align}
	Substituting inequalities \eqref{eqn:I1Bound}, \eqref{t5} and \eqref{eqn:I3Bound} 
	on equation \eqref{eqn:IntErrToBound}, we deduce that
	\begin{equation*}
		\EX{
			\sup_{0\leq s \leq t}	
			|e(t)|^2
		}
		\leq
			L \int_0^t
				\m |e(s)|^2 ds
			+
			L h^2 
		\leq		
			L \int_{0}^t
				\EX{
					\sup_{0\leq r \leq s}
					|e(s)|^2	
				}ds
			+Lh^2.		
	\end{equation*}
	By the Gronwall inequality, we conclude that
	\begin{equation*}
		\EX{
			\sup_{0 \leq t \leq T} 	
			|e(t)|^2
		}
		\leq
			L  \exp(LT) h^2 \leq C h^2.
	\end{equation*} 	
		\qed
\end{pf}

	We  can now obtain the convergence rate of the explicit Linear Steklov method.

\begin{thm}
	Consider the \SM method applied to SDE \eqref{eqn:SDE1} and under \Crefrange{ass:OSLC}{PolynomialGrowth}.
	Then there exist a continuous extension $\overline{Y}(t)$ of the LS numerical approximation for which
	\begin{equation*}
		\EX{
			\sup_{0 \leq t \leq T}
			|\overline{Y}(t) - y(t)|^2	
		} = \mathcal{O}(h).	
	\end{equation*}
\end{thm}
\begin{pf}
	 We can bound
	\begin{align*}
		\EX{
			\sup_{0 \leq t \leq T}	
			|\overline{Y}(t) - y(t)|^2
		}
		%
		&\leq 
		2 \EX{
			\sup_{0 \leq t \leq T}	
			|\overline{Y}(t) - y_h(t)|^2
		}
		+
		2 \EX{
			\sup_{0 \leq t \leq T}	
			|y_h(t) - y(t) |^2
		}.\\		
	\end{align*}	
	By \Cref{lem:yhyOh} we have
	$$
		\EX{
			\sup_{0 \leq t \leq T}	
			|y_h(t) - y(t) |^2 
		}= \mathcal{O}(h^2),
	$$
	then it remains to prove that 
	$$
		\EX{
			\sup_{0 \leq t \leq T}	
			|\overline{Y}(t) - y_h(t)|^2
		},
	$$
	but  $\overline{Y}(t)$ can be regarded as the EM applied to the modified SDE \eqref{eqn:SDEMod}, and by
	Lemmas \eqref{lem:BoundAndConvergenceOfyh},\eqref{lem:SSSMMomentBounds} and \Cref{col:ContinuousExtBoundedMoments}
	$y_h$ ,$Y_k$ and $\overline{Y}(t)$ has bounded moments, then adapting the proof of 
	\Cref{thm:EulerConvergenceRateHMS} (see \cite[Thm. 4.4]{Higham2002b}) we can deduce that
	\begin{equation*}
		\EX{
			\sup_{0 \leq t \leq T}	
			|\overline{Y}(t) - y_h(t)|^2
		} = \mathcal{O}(h).
	\end{equation*}
	as we require. \qed
\end{pf}
%
%********************************************************************************************
%              Section 7
%********************************************************************************************
